---
title: "Complexity"
author: "peter"
date: "2024-04-30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r warning=FALSE, message=FALSE}
library(tidyverse)
library(ggtext)
```

### Algorithms: Big O 
[ https://en.wikipedia.org/wiki/Big_O_notation ]

```{r }

n=1:20

y1 = n * log(n)
y2 = choose(n,3)
y3 = 2^n
```



### Plots show that some algorithms do not scale well with n.

```{r warning=FALSE, message=FALSE}
df = tibble(y1=y1, y2=y2, y3=y3)

ggplot(df, aes(x=n)) +
  ylim(0,1200) +
  geom_line(aes(y=y1, colour = "y1"))  + 
  geom_line(aes(y=y2, colour = "y2")) +
  geom_line(aes(y=y3, colour = "y3"))   +
  scale_colour_manual("", values = c("y1"="blue", "y2"="green", "y3"="red"),
                      labels=c("n log n", "n choose m", expression(paste(2^n))), name="Big O") +
  labs(x = "n", y = "time") +
  theme_minimal() + theme(plot.title = element_text(size = 15)) +
  ggtitle("Complexity depends on n, m=3") 
  

mainDir="."
subDir="figures"
dir.create(file.path(mainDir, subDir), showWarnings = FALSE)
#ggsave(filename = "./figures/Big-O.pdf")
```
### PDF of an exponential distribution

The exponential distribution or negative exponential distribution is the probability distribution of the distance between events in a Poisson point process, i.e., a process in which events occur continuously and independently at a constant average rate.

The distance parameter could be any meaningful mono-dimensional measure of the process, such as time between production errors, or length along a roll of fabric in the weaving manufacturing process. It is a particular case of the gamma distribution. 

```{r}
lambda = .25   # arrival rate, e.g. . 1 error per 4 hours
x = seq(1,15, .1)
p = lambda * exp(-lambda*x)

df=tibble(x,p)

ggplot(df, aes(x=x) ) + 
  geom_line(aes(y=p)) +
  labs(x = "x (time between production errors", y = "p(x)") +
  theme_minimal() + theme(plot.title = element_text(size = 15)) +
  ggtitle("PDF: exponential function") 
```

